%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventry
    {Software Engineer} % Job title
    {Tapestry Solutions} % Organization
    {St. Louis, MO} % Location
    {February 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Solved issues with and created new features for OneSAF, an interactive military training simulator, using Java in Linux environment.}
        \item {Implemented new features for Chinook Mission Planning Software in C\#.}
        \item {Participated in daily standups as part of Agile team.}
        \item {Utilized Git VCS on a near daily basis.}
        \item {Spoke with customers to develop user stories, clarify objective and share progress on ongoing tasks.}
        \item {Developed suite of JUnit automated tests to run alongside nightly builds on Jenkins.}
      \end{cvitems}
    }

  \cventry
    {Customer Service} % Job title
    {Lowe's Home Improvement} % Organization
    {Maplewood, MO} % Location
    {March - August 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Mastered the use of the internal software systems.}
        \item {Facilitated the exchange of fragile and expensive merchandise in a fast paced environment.}
      \end{cvitems}
    }

  \cventry
    {Customer Service} % Job title
    {Best Buy} % Organization
    {Chesterfield, MO} % Location
    {October 2016 - February 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Quickly became proficient in the use of several company applications (ETK, OMS, POS).}
        \item {Communicated effectively with customers of varying technical backgrounds to ensure they leave with the products they need.}
      \end{cvitems}
    }

%---------------------------------------------------------

\vspace{-2mm}

\end{cventries}
